Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller \textbf{{Shanghai version \YellowPaperVersionNumber}}

### 2025-02-10 Paper.tex

Early work on smart contracts has been done by \cite{szabo1997formalizing} and \cite{miller1997future}. Around the 1990s it became clear that algorithmic enforcement of agreements could become a significant force in human cooperation. Though no specific system was proposed to implement such a system, it was proposed that the future of law would be heavily affected by such systems. In this light, Ethereum may be seen as a general implementation of such a \textit{crypto-law} system.

@@

0x30 & {\small ADDRESS} & 0 & 1 & Get address of the current account. \\

>>>>

Early work on smart contracts has been done by \cite{szabo1997formalizing} and \cite{miller1997future}. Around the 1990s, it became clear that algorithmic enforcement of agreements could become a significant force in human cooperation. Though no specific system was proposed to implement such a system, it was proposed that the future of law would be heavily affected by such systems. In this light, Ethereum may be seen as a general implementation of such a \textit{crypto-law} system.

@@

0x30 & {\small ADDRESS} & 0 & 1 & Get address of currently executing account. \\
